Generalized Tractability

### 2023-06-04 Older_versions/GeneralizedTractability_230501.tex
Updates from Overleaf

\begin{example}[Algebraic polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)= \max\{1,\varepsilon^{-p}\}\, d^q
 \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2, 
\] where in this case $\vp = (p,q)$.
Then Theorem \ref{thm_main_tract2} yields the  equivalent condition for algebraic polynomial tractability:
\[
 \sup_{d\in\naturals} \sum_{i=L_{(p,q)} d^{q}}^\infty (\min\{1,\lambda_{i,d}^p\}) d^{-q} < \infty \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
\]
Furthermore, the set of optimal $(p,q)$ is a subset of
\begin{multline*}
\{(p^*,q^*) : \text{the above condition holds for all }(p,q) \in (p^*,\infty) \times (q^*,\infty) \\
\text{but not for any }(p,q) \in [0,p^*/2) \times [0,q^*/2)\}.
\end{multline*}
This essentially recovers the result on polynomial tractability in \cite[Theorem 5.1]{NW08} \fred{same theorem as above??, what about optimality in \cite[Theorem 5.1]{NW08}}.
\end{example}

\begin{example}[Strong exponential polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)= \left[\max\{1,\log(1+\varepsilon^{-1})\}\right]^p, \quad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
\]
where $\vp$ is a scalar. Then Theorem \ref{thm_main_strong_tract2} yields the equivalent condition for strong exponential polynomial tractability \[
 \sup_{d\in\naturals} \sum_{i=L_{p} }^\infty (\min\{1,\log(1+\lambda_{i,d}\})^{p}  < \infty,\quad  \text{ for some } p \ge 0, L_{p} \in \naturals
\] In this case the optimal $p$ is the infimum of all $p$ for which the above condition holds.
\end{example}
\begin{example}[Exponential polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)=\left[\max\{1,\log(1+\varepsilon^{-1}\})\right]^p\, d^q, \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2, 
\] where $\vp = (p,q)$. Then Theorem \ref{thm_main_tract2} yields  the equivalent condition for exponential polynomial tractability
\[
 \sup_{d\in\naturals} \sum_{i=L_{(p,q)} d^{q}}^\infty [\min\{1,\log(1+\lambda_{i,d}\})]^p d^{-q} < \infty  \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
\]
\end{example}

\begin{example}[Algebraic quasi-polynomial tractability] Here we consider another common notions of tractability.

@@

\noindent Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\varepsilon^{-1}\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
\] where in this case $\vp = p$. This can be rewritten as 
\[
T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\varepsilon^{-1}\}]^{p(1+\log d)}d^p
\]
Observe that the function $T$ is a function of $\max\{1,\varepsilon^{-1}\}$ and $d$ which are, polynomial or not exponential in powers of $\max\{1,\varepsilon^{-1}\}$ and $d$. Hence we can apply Theorem \ref{thm_main_tract2} as follows. We have the following equivalent condition for quasi-polynomial tractability in the algebraic case
\[
\sup_{d\in\mathbb{N}}\sum_{i=Lp\,e^pd^{p}} \left(\min\{1,\lambda_{i,d}\} \right)^{p(1+\ln d)}e^{-p}d^{-p} < \infty \qquad \text{for some} p \geq 0, L_p \in \naturals.
\]
\end{example}
\begin{example}[Exponential quasi-polynomial tractability]

@@

\kachi{In the following we introduce two specific cases of tractability which depend on the form of the function $T$.
\begin{example}[(Strong) Separable tractability]
Suppose that
\[
 T(\varepsilon^{-1},d,\vp)= \phi(\varepsilon^{-1},p)\, \psi(d,q)
 \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2.
\]
with non-decreasing functions $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$ and where $\vp = (p,q)$.

We say that a problem is defined as $T$-separable tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ which does not depend on $\varepsilon$ and $d$ such that
\[
\comp(\varepsilon,d) \leq  C_{\vp}\,T(\varepsilon^{-1},d,\vp)\qquad \forall \varepsilon >0, \, d\in\naturals,
\]
that is
\[
\comp(\varepsilon,d) \leq \phi(\varepsilon^{-1},p)\, \psi(d,q) \qquad \forall \varepsilon >0, \, d\in\naturals.
\]
A problem is strongly $T$-separable tractable with parameter $\vp$ iff the complexity is independent of $d$, that is, there exists a positive constant $C_{\vp}$ which again does not depend on $\varepsilon$ and $d$ such that
\[
\comp(\varepsilon,d) \leq C_{\vp}T(\varepsilon^{-1}, 1,\vp) \qquad \forall \varepsilon >0, \, d\in\naturals,
\] where $\vp = p$. We have
\[
\comp(\varepsilon,d) \leq \phi(\varepsilon^{-1},p)\qquad \forall \varepsilon >0, \, d\in\naturals.
\]
%In addition, we assume the following conditions as in (\ref{eq:ptauassume}). That is, there exists a $K_{(p,q),\tau}$ depending on $p,q$ and $\tau$, but independent of $\varepsilon$ and $d$, such that
%\begin{equation} \label{eq:tractiff}    \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = C(p,q)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p))} < \infty.\end{equation}
Furthermore, we assume that
\[
\lim_{\varepsilon\rightarrow0}T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d\in\naturals, \vp \in[0,\infty)^2.
\]
Also since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit
\[
T(0,d,\vp):= \lim_{\varepsilon \rightarrow \infty}T(\varepsilon^{-1},d,\vp)\geq T(0,1,\textbf{0})>0
\] 
%Furthermore, we assume the following technical conditions. There exists a $K_{(p,q),\tau}$ depending on $p,q$ and $\tau$, but independent of $\varepsilon$ and $d$, such that
\begin{align*}
     [\phi(\varepsilon^{-1},p)]^{\tau} &\le K_{(p,1),\tau} \phi (\varepsilon^{-1},\tau p)\\
      [\psi(d,q)]^{\tau} &\le K_{(1,q),\tau} \psi (d,\tau q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals,\, p,q\geq 0,\, \tau >0.
\end{align*}
%\begin{align*}
 %  [T(\varepsilon^{-1},d,\vp]^\tau \leq K_{\vp,\tau}T(\varepsilon^{-1},d,\tau\vp) \quad \forall \varepsilon \in (0,\infty),\, d\in \mathbb{N},\, \vp\in[0,\infty)^2, \tau >0\end{align*}
Thus, Theorem \ref{thm_main_strong_tract2} yields the following equivalent condition for strongly separable tractability
\begin{equation*} \label{eq:strong_tractiff}
     \sup_{d \in \naturals} \sum_{i = L_p}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty.
\end{equation*}
Theorem \ref{thm_main_tract2} yields the following equivalent condition for 
separable tractability
\[
 \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = L_{(p,q)\psi(d,q)}}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty.
\]
%As the name implies, the roles of $\varepsilon^{-1}$ and $d$ are separated. 
\end{example}
\begin{example}[Non-separable tractability]
    Let the tractability function $T$, be defined by
\[
 T(\varepsilon^{-1},d,\vp)= \exp\{p(\phi(\varepsilon^{-1})\, \psi(d))\}
 \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp\in [0,\infty).
\]  with non-decreasing functions $\phi : (0,\infty) \to (0,\infty)$ and $\psi : \naturals \to (0,\infty)$ and $\vp = p$. Furthermore, we assume the following technical conditions. There exists a $K_{(p,q),\tau}$ depending on $p,q$ and $\tau$, but independent of $\varepsilon$ and $d$, such that
\begin{align*}
     [\phi(\varepsilon^{-1},p)]^{\tau} &\le K_{(p,1),\tau} \phi (\varepsilon^{-1},\tau p)\\
      [\psi(d,q)]^{\tau} &\le K_{(1,q),\tau} \psi (d,\tau q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals,\, p,q\geq 0,\, \tau >0.
\end{align*}
\end{example}
}

@@

Suppose that the domain of interesting $(\varepsilon^{-1},d)$ is not all of $(0,\infty \times \naturals$ but given by 
\begin{equation}
    \Omega  = \{(\varepsilon^{-1},d) : \varepsilon > E(d) \ge 0, \ d \in \naturals \},
\end{equation}
where $E$ is a non-increasing function.  A problem is
$T$-tractable with parameter $\vp$ \emph{on the restricted domain $\Omega$} iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:rest_strong_tract_def}
	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},1,\vp) \qquad \forall(\varepsilon^{-1},d) \in \Omega.
\end{equation}
Define $M(d) = \max\{n : \lambda_{n+1,d} \ge E(d)\}$, i.e., 
\[
\lambda_{1,d}\ge  \cdots \ge \lambda_{M(d)+1,d} \ge E(d) > \lambda_{M(d)+2,d}, \qquad
(\lambda_{1,d}^{-1},d), \ldots, (\lambda^{-1}_{M(d)+1,d},d)  \in \Omega.
\]

@@

Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d,\vp)$ are non-decreasing in $i$ for $i \in \{1, \ldots, M(d)+1\}$. In particular, for  any $n \in \{N, \ldots, M(d)\}$
\begin{align*}
    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{N,d}
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d,\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},d,\vp)} \\
     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp) }
    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},d,\vp) }
    \le \frac{1}{n-N+1} \sum_{i=N}^{M(d)}  \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}.
\end{align*}
Thus, we can conclude from the previous line that
\begin{multline} \label{eq:implicate_a_rest}
    n - N +1 \ge T(\varepsilon^{-1},d,\vp) \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)} \\
   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp)} \le
   \frac{1}{n-N+1} \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp) } \le \frac{1}{T(\varepsilon^{-1},d,\vp)} \\ \forall d, n, N \in \naturals.
\end{multline}
We note that the left side of the implication implies $n \ge N$ automatically since $n$ is an integer  $n - N +1$ is assumed to be positive.

@@

it follows from \eqref{eq:compUP} with $N = \lceil L_{\vp}\, T(0,d,\vp)\rceil$ that 
\begin{align*}
       \comp(\varepsilon,d)
       & \le T(\varepsilon^{-1},d,\vp) \Biggl [ 
       \frac{\lceil L_{\vp}\, T(0,d,\vp)\rceil}{T(\varepsilon^{-1},d,\vp)}  + 
       \underbrace{\sum_{i=\lceil L_{\vp}\, T(0,d,\vp)\rceil}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} \text{ by \eqref{eq:rest_tractiff4}}}
       \Biggr ] 
        \quad \forall \varepsilon > 0, \ d  \in \naturals\\
       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{L_{\vp} T(0,d,\vp)+1}{T(\varepsilon^{-1},d, \vp)} +  S_{\vp} \right]
        \qquad \forall \varepsilon > 0, \ d  \in \naturals\\
       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{L_{\vp} T(0,d,\vp)}{T(\varepsilon^{-1},d, \vp)}
       + \frac{1}{T(0,1, \vp)} + S_{\vp}\right]
       \qquad \text{by \eqref{eq:Tnondecreasing}}   \\
       & \le T(\varepsilon^{-1},d,\vp) 
       \underbrace{\left [  L_{\vp} + \frac{1}{T(0,1, \vp)} + S_{\vp} \right]}_{=:C_{\vp}}
       \qquad \text{by \eqref{eq:Tnondecreasing}}  
\end{align*}
It follows that we have $T$-tractability, which shows sufficiency of \eqref{eq:rest_tractiff4}.

@@

\noindent \textbf{Necessary condition:}\\
Suppose that we have
$T$-tractability. That is, for some $\vp \ge \vzero$, there exists a positive constant $C_{\vp}$ such that
\[
\comp(\varepsilon,d)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall (\varepsilon^{-1}, d) \in \Omega.
\]
Since the sequence of eigenvalues $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
\begin{equation}\label{eq:lambda_K4}
	\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon \qquad 
 \forall (\varepsilon^{-1}, d) \in \Omega.
\end{equation}
Define the integers \fred{Only got here because we have to be careful with the domain of stuff}
\[
i (\varepsilon,d,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1, \qquad
i (\infty,d,\vp) := \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \ge 1.
\]
Thus, it follows by \eqref{eq:lambda_K4} that $\lambda_{i(\varepsilon,d,\vp),d} \le \varepsilon$.
Note furthermore that we always have
\[
i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1, \qquad \forall \varepsilon > 0, \ d \in \naturals,
\]
since
$T(\cdot,d,\vp)$ is non-decreasing.

>>>>

\begin{example}[Algebraic polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)= \max\{1,\varepsilon^{-p}\}\, d^q
 \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2, 
\] where in this case $\vp = (p,q)$.
Then Theorem \ref{thm_main_tract2} yields the  equivalent condition for algebraic polynomial tractability:
\[
 \sup_{d\in\naturals}\, d^{-q} \sum_{i=L_{(p,q)} d^{q}}^\infty (\min\{1,\lambda_{i,d}^p\})  < \infty \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
\]
Furthermore, the set of optimal $(p,q)$ is a subset of
\begin{multline*}
\{(p^*,q^*) : \text{the above condition holds for all }(p,q) \in (p^*,\infty) \times (q^*,\infty) \\
\text{but not for any }(p,q) \in [0,p^*/2) \times [0,q^*/2)\}.
\end{multline*}
This essentially recovers the result on polynomial tractability in \cite[Theorem 5.1]{NW08} \fred{same theorem as above??, what about optimality in \cite[Theorem 5.1]{NW08}}.
\end{example}

\begin{example}[Strong exponential polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)= \left[\max\{1,\log(1+\varepsilon^{-1})\}\right]^p, \quad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
\]
where $\vp$ is a scalar. Then Theorem \ref{thm_main_strong_tract2} yields the equivalent condition for strong exponential polynomial tractability \[
 \sup_{d\in\naturals} \sum_{i=L_{p} }^\infty (\min\{1,\log(1+\lambda_{i,d}\})^{p}  < \infty,\quad  \text{ for some } p \ge 0, L_{p} \in \naturals
\] In this case the optimal $p$ is the infimum of all $p$ for which the above condition holds.
\end{example}
\begin{example}[Exponential polynomial tractability]
Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)=\left[\max\{1,\log(1+\varepsilon^{-1}\})\right]^p\, d^q, \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2, 
\] where $\vp = (p,q)$. Then Theorem \ref{thm_main_tract2} yields  the equivalent condition for exponential polynomial tractability
\[
 \sup_{d\in\naturals}\, d^{-q} \sum_{i=L_{(p,q)} d^{q}}^\infty [\min\{1,\log(1+\lambda_{i,d}\})]^p < \infty  \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
\]
\end{example}

\begin{example}[(Strong) Separable tractability]
Suppose that the tractability function is defined by
\[
 T(\varepsilon^{-1},d,\vp)= \phi(\varepsilon^{-1},p)\, \psi(d,q)
 \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2.
\]
with non-decreasing functions $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$ and where $\vp = (p,q)$, hence $T$ is non-decreasing in all variables.

We say that a problem is defined as $T$-separable tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ which does not depend on $\varepsilon$ and $d$ such that
\[
\comp(\varepsilon,d) \leq  C_{\vp}\,\phi(\varepsilon^{-1},p)\, \psi(d,q)\qquad \forall \varepsilon >0, \, d\in\naturals.
\]
A problem is strongly $T$-separable tractable with parameter $\vp$ iff the complexity is independent of $d$, that is, there exists a positive constant $C_{\vp}$ which again does not depend on $\varepsilon$ and $d$ such that
\[
\comp(\varepsilon,d) \leq C_{\vp}\phi(\varepsilon^{-1},p)\psi(1,q) \qquad \forall \varepsilon >0, \, d\in\naturals,
\] where $\vp = (p,q)$. 
Furthermore, we assume the following as in \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.
\[
\lim_{\varepsilon\rightarrow0}\phi(\varepsilon^{-1},p) = \infty \qquad \forall d\in\naturals, p >0.
\]
Also since $T(\cdot,d,\vp)$ is non-decreasing, we define the following limit
\[
T(0,d,\vp):= \lim_{\varepsilon \rightarrow \infty}T(\varepsilon^{-1},d,\vp)\geq T(0,1,\textbf{0})>0
\] 
Additionally, we have the following technical assumptions. Suppose that, for any real $\tau_1, \tau_2>0$ and any $p,q>0$, we have that 
\begin{align*}
     [\phi(\varepsilon^{-1},p)]^{\tau_1} &\le \hat{K}_{p,\tau_1} \phi (\varepsilon^{-1},\tau_1 p)\\
      [\psi(d,q)]^{\tau_2} &\le \hat{K}_{q,\tau_2} \psi (d,\tau_2 q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals.
\end{align*} where $L_{p,\tau_1}>0$ is a constant that may depend on $p$ and $\tau_1$, but is independent of $\varepsilon$, and where $L_{q,\tau_2}>0$ is a constant that may depend on $q$ and $\tau_2$, but is independent of $d$.
\begin{align*}
  [T(\varepsilon^{-1},d,\vp]^\tau \leq K_{\vp,\tau}T(\varepsilon^{-1},d,\tau\vp) \quad \forall \varepsilon \in (0,\infty),\, d\in \mathbb{N},\, \vp\in[0,\infty)^2, \tau >0\end{align*}

Thus, Theorem \ref{thm_main_strong_tract2} yields the following equivalent condition for strongly separable tractability
\begin{equation*} \label{eq:strong_tractiff}
     \sup_{d \in \naturals} \sum_{i = L_p}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty.
\end{equation*}
Theorem \ref{thm_main_tract2} yields the following equivalent condition for 
separable tractability
\[
 \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = L_{(p,q)\psi(d,q)}}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty.
\]
%As the name implies, the roles of $\varepsilon^{-1}$ and $d$ are separated.

\end{example}

\begin{example}[Non-separable tractability]
    Let the tractability function $T$, be defined by
\[
 T(\varepsilon^{-1},d,\vp)= \exp\{p(\phi(\varepsilon^{-1})\, \psi(d))\}
 \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp\in [0,\infty).
\]  with non-decreasing functions $\phi : (0,\infty) \to (0,\infty)$ and $\psi : \naturals \to (0,\infty)$ and $\vp = p$. 
We say that a problem is non-separable tractable with parameter $\vp$ iff there exists a positive $C_{\vp}$ such that
\[
\comp(\varepsilon,d) \leq C_{\vp} T(\varepsilon^{-1},d,\vp),
\]
for all $\varepsilon\in (0,1]$ and $d\in \naturals$, that is
\[\comp(\varepsilon,d) \leq  \exp\{p(\phi(\varepsilon^{-1})\psi(d))\}.\]

Hence we can apply Theorem \ref{thm_main_tract2} as follows. We have the following equivalent condition for non-separable tractability
\[
\sup_{d\in\mathbb{N}}\sum_{i=Lp\,\psi(d)} \phi(\lambda_{i,d})\psi(d) < \infty \qquad \text{for some} p \geq 0, L_p \in \naturals.
\]
We have the following special cases. \end{example}
\begin{example}[Algebraic quasi-polynomial tractability] Here we consider another common notions of tractability.

@@

\noindent Let the tractability function, $T$,
be defined by
\[
 T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\varepsilon^{-1}\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
\] where in this case $\vp = p$. This can be rewritten as 
\[
T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\varepsilon^{-1}\}]^{p(1+\log d)}d^p
\]
Observe that the function $T$ is a function of $\max\{1,\varepsilon^{-1}\}$ and $d$ which are, polynomial or not exponential in powers of $\max\{1,\varepsilon^{-1}\}$ and $d$. Hence we can apply Theorem \ref{thm_main_tract2} as follows. We have the following equivalent condition for quasi-polynomial tractability in the algebraic case
\[
\sup_{d\in\mathbb{N}}\frac{1}{d^p}\sum_{i=Lp\,d^{p}} \left(\min\{1,\lambda_{i,d}\} \right)^{p(1+\ln d)} < \infty \qquad \text{for some } p \geq 0, L_p \in \naturals.\]
\end{example}
\begin{example}[Exponential quasi-polynomial tractability]

@@

%In the following we introduce two specific cases of tractability which depend on the form of the function $T$ (see \cite{}).

@@

Suppose that the domain of interest $(\varepsilon^{-1},d)$ is not all of $(0,\infty) \times \naturals$ but given by 
\begin{equation}
    \Omega  = \{(\varepsilon^{-1},d) : \varepsilon \peter{\ge E(d) > 0}, \ d \in \naturals \},
\end{equation}
where $E$ is a non-increasing \peter{[{is this a necessary assumption?}]} function.  A problem is \peter{strongly}
$T$-tractable with parameter $\vp$ \emph{on the restricted domain $\Omega$} iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:rest_strong_tract_def}
	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},1,\vp) \qquad \forall(\varepsilon^{-1},d) \in \Omega.
\end{equation}
\peter{[I am wondering whether this makes sense if $E$ depends on $d$? Do Gnewuch and Wo\'{z}niakowski allow dependence of $E$ on $d$?]}

\peter{
A problem is 
$T$-tractable with parameter $\vp$ \emph{on the restricted domain $\Omega$} iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
\begin{equation} \label{eq:rest_tract_def}
	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall(\varepsilon^{-1},d) \in \Omega.
\end{equation}
}

Define $M(d) = \max\{n : \lambda_{n+1,d} \ge E(d)\}$, i.e., 
\[
\lambda_{1,d}\ge  \cdots \ge \lambda_{M(d)+1,d} \ge E(d) > \lambda_{M(d)+2,d}, \qquad
(\lambda_{1,d}^{-1},d), \ldots, (\lambda^{-1}_{M(d)+1,d},d)  \in \Omega.
\]

@@

Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d,\vp)$ are non-decreasing in $i$ for $i \in \{1, \ldots, M(d)+1\}$. In particular, for any \peter{$N\in\{1,\ldots,M(d)\}$ and any} $n \in \{N, \ldots, M(d)\}$
\begin{align*}
    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{N,d}
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d,\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},d,\vp)} \\
     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp) }
    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},d,\vp) }
    \le \frac{1}{n-N+1} \sum_{i=N}^{M(d)}  \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}.
\end{align*}
Thus, we can conclude from the previous line that
\begin{multline} \label{eq:implicate_a_rest}
    n - N +1 \ge T(\varepsilon^{-1},d,\vp) \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)} \\
   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp)} \le
   \frac{1}{n-N+1} \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp) } \le \frac{1}{T(\varepsilon^{-1},d,\vp)} \\ \forall d, n, N \in \naturals.
\end{multline}
We note that the left side of the implication implies $n \ge N$ automatically since $n$ is an integer and $n - N +1$ is assumed to be positive.

@@

it follows from \eqref{eq:compUP_rest} with $N = \lceil L_{\vp}\, T(0,d,\vp)\rceil$ that 
\begin{align*}
       \comp(\varepsilon,d)
       & \le T(\varepsilon^{-1},d,\vp) \Biggl [ 
       \frac{\lceil L_{\vp}\, T(0,d,\vp)\rceil}{T(\varepsilon^{-1},d,\vp)}  + 
       \underbrace{\sum_{i=\lceil L_{\vp}\, T(0,d,\vp)\rceil}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} \text{ by \eqref{eq:rest_tractiff4}}}
       \Biggr ] 
        \quad \forall \varepsilon > 0, \ d  \in \naturals\\
       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{L_{\vp} T(0,d,\vp)+1}{T(\varepsilon^{-1},d, \vp)} +  S_{\vp} \right]
        \qquad \forall \varepsilon > 0, \ d  \in \naturals\\
       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{L_{\vp} T(0,d,\vp)}{T(\varepsilon^{-1},d, \vp)}
       + \frac{1}{T(0,1, \vp)} + S_{\vp}\right]
       \qquad \text{by \eqref{eq:Tnondecreasing}}   \\
       & \le T(\varepsilon^{-1},d,\vp) 
       \underbrace{\left [  L_{\vp} + \frac{1}{T(0,1, \vp)} + S_{\vp} \right]}_{=:C_{\vp}}
       \qquad \text{by \eqref{eq:Tnondecreasing}}  
\end{align*}
It follows that we have $T$-tractability, which shows sufficiency of \eqref{eq:rest_tractiff4}.

@@

\noindent \textbf{Necessary condition:}\\
Suppose that we have
$T$-tractability. That is, for some $\vp \ge \vzero$, there exists a positive constant $C_{\vp}$ such that
\[
\comp(\varepsilon,d)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall (\varepsilon^{-1}, d) \in \Omega.
\]
Since the sequence of eigenvalues $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
\begin{equation}\label{eq:lambda_K4}
	\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon \qquad 
 \forall (\varepsilon^{-1}, d) \in \Omega.
\end{equation}
Define the integers \fred{Only got here because we have to be careful with the domain of stuff.} 
\peter{[PETER: Adding something we might use in color, but not deleting any of the things we already have.]}
\[
i (\varepsilon,d,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1, \qquad
i (\infty,d,\vp) := \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \ge 1.
\]

It follows by \eqref{eq:lambda_K4} that $\lambda_{i(\varepsilon,d,\vp),d} \le \varepsilon$.
Note furthermore that we always have
\[
i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1, \qquad \forall \varepsilon > 0, \ d \in \naturals,
\]
since
$T(\cdot,d,\vp)$ is non-decreasing
\peter{{[Actually, the }same should hold $\forall (\varepsilon^{-1},d)\in\Omega$, right? ]} .

For $\varepsilon$ taking on all positive values \peter{(values in $[E(d),\infty)$)}, $i(\varepsilon,d,\vp)$ takes on all values greater than or equal to $i(\infty,d,\vp)$
\peter{(in $\{i(\infty,d,\vp),\ldots, i(E(d),d,\vp)\}$)}, so
\[
i\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i,d}^{-1},d,\vp)+1, \qquad \forall i \ge i(\infty,d,\vp),  \ d \in \naturals.
\]
\peter{[Could we not go through the same argument as below with $i$ being in the set $\{i(\infty,d,\vp),\ldots, i(E(d),d,\vp)\}$?]}

This implies via our technical assumption \eqref{eq:ptauassume} that for any $\tau > 1$,
\begin{gather*}
	K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},d,\tau \vp) \ge
	[T(\lambda_{i,d}^{-1},d, \vp)]^\tau
	\ge
	\left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i \ge i(\infty,d,\vp),  \ d \in \naturals, \\
	 \frac{1}{T (\lambda_{i,d}^{-1},d,\tau \vp)} \le
	\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \max\{i(\infty,\vp),2\},  \ d \in \naturals.
\end{gather*}
